The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
disc draft

\subsection{Contribution to Academia} 
%       -How will our study help other researchers?
%       -How are the results valuable?

@@

@@

%Implications for Industry
%Important to understand the types of changes they are making so that they can better plan for them in the future. Design around them, design for them? Design to minimise them? Spin this into a design problem? **According to Lehman's laws, systems must keep changing otherwise they decline in quality. If they wish to maintain the quality of their system and provide new features, it would be helpful to know what kinds of changes are common for their APIs.
%Implications for Academia
%Future work / suggestions based on this RQ?

@@

1. Small intro which: Summarises the findings of the discussion

2. Conclusions/outcomes:
Industry
Have a more structured feedback loop (include users) this can be future work too
              Greater emphasis should be placed upon communicating with the end users / application developers. They should probably improve their feedback system to get more feedback from the API users.
              Include more scientific theories
              --> consider ecosystem stuff

Academia
Some laws dont apply. Propose a new version of the law.
Interesting that hardware did not drive change. This is cool cuz it means hardware apis can be generalised to any type of api.
Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies
%%William add conclusion ideas here
That the part about controlling how the API users use the API was such an important thing is interesting. (Not something we expected). 
       MAke a study which looks the quality of applications before and after api changes have been introduced

3. Future work: Summarise what the next steps could be.
Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
       -->Suggest a similar study which looks at business factors
 in-depth study on each of the laws (more exhaustive) (suggested by Imed during Friday review)

Random tips n trickz:
       Look up the papers from the conference (especially regarding the discussion/conclusion)
       discussion = revisiting research questions (and maybe structuring around industry/academia)
       conclusion = summary part, main final points and future work 
       look up implications for practitioners 
       recommendations for the case company (need to put this somewhere)

>>>>

\subsection{Contribution to Academia} 
Some laws don't apply. Consider inverting the law of org stab for APIs
Since motives are reverse engineerable, it hsould encourage more ppl to do similar studies

%       -How will our study help other researchers?
%       -How are the results valuable?

@@

3. Suggest to Axis that they improve their feedback loop by using the types

Also suggest that they keep evolving the API with reference to the laws

@@

@@

1. Summary of our results/discussion i.e. short conclusion

2. Future work:
       a) Eco-system (rel. to feedback loop law and Chapin/Swanson communication to stakeholders)
       b) Business motives instead of evolution theories
       c) A study which analyses how the API applications change when new versions are introduced (rel. to controlling the behaviour etc.)

       In-depth study on the laws or a specific law? Maybe less interesting.
